### 2021-08-20 data/draft-publications.tex
filter corrected

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\item Addario-Berry, Louigi and Bhamidi, Shankar and Sen, Sanchayan: A probabilistic approach to the leader problem in random
graphs, \emph{Random Structures Algorithms} {\bf 58} (2021), 34--67.

@@

\item Adhikari, Saswata and Anoop, V. P. and Parui, Sanjay: Existence of extremals of {D}unkl-type {S}obolev inequality
and of {S}tein-{W}eiss inequality for {D}unkl {R}iesz
potential, \emph{Complex Anal. Oper. Theory} {\bf 15} (2021), Paper No. 28, 34.

@@

\item Anoop, V. P. and Parui, Sanjay: Improved fractional {H}ardy inequalities for {D}unkl gradient, \emph{Math. Inequal. Appl.} {\bf 24} (2021), 129--155.
\item Arunkumar, G.: Chromatic symmetric function of graphs from {B}orcherds
algebras, \emph{J. Combin. Theory Ser. A} {\bf 183} (2021), Paper No. 105492, 28.

@@

\item Balodi, Mamta and Banerjee, Abhishek and Ray, Samarpita: Entwined modules over linear categories and {G}alois
extensions, \emph{Israel J. Math.} {\bf 241} (2021), 623--692.

@@

\item Banerjee, Abhishek: {$FI$}-modules over preadditive categories and torsion
theories, \emph{J. Pure Appl. Algebra} {\bf 225} (2021), 106595, 29.

@@

\item Banerjee, Agnid and Garofalo, Nicola and Manna, Ramesh: A strong unique continuation property for the heat operator
with {H}ardy type potential, \emph{J. Geom. Anal.} {\bf 31} (2021), 5480--5504.

@@

\item Basak, Riju and Garg, Rahul and Thangavelu, Sundaram: Homogeneous {F}ourier and {W}eyl multipliers on {S}obolev
spaces related to the {H}eisenberg group, \emph{J. Funct. Anal.} {\bf 281} (2021), Paper No. 109154, 45.

@@

\item Basu, Riddhipratim and Ganguly, Shirshendu and Hegde, Milind
and Krishnapur, Manjunath: Lower deviations in {$\beta$}-ensembles and law of iterated
logarithm in last passage percolation, \emph{Israel J. Math.} {\bf 242} (2021), 291--324.
\item Behera, Kiran Kumar: A generalized inverse eigenvalue problem and {$m$}-functions, \emph{Linear Algebra Appl.} {\bf 622} (2021), 46--65.

@@

\item Bera, Sudip: Enumeration of weighted paths on a digraph and block hook
determinant, \emph{Spec. Matrices} {\bf 9} (2021), 197--211.
\item Bera, Sudip and Dey, Hiranya Kishore and Mukherjee, Sajal
Kumar: On the connectivity of enhanced power graphs of finite groups, \emph{Graphs Combin.} {\bf 37} (2021), 591--603.

@@

\item Bhattacharyya, Tirthankar and Das, B. Krishna and Sau,
Haripada: Toeplitz operators on the symmetrized bidisc, \emph{Int. Math. Res. Not. IMRN} {\bf } (2021), 8492--8520.

@@

\item Biswas, Anindya and Maitra, Anwoy: A characterization of the bidisc by a subgroup of its
automorphism group, \emph{J. Math. Anal. Appl.} {\bf 504} (2021), Paper No. 125434, 10.

@@

\item Carstensen, Carsten and Mallik, Gouranga and Nataraj, Neela: Nonconforming finite element discretization for semilinear
problems with trilinear nonlinearity, \emph{IMA J. Numer. Anal.} {\bf 41} (2021), 164--205.

@@

\item Chattopadhyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: Multiplicities, invariant subspaces and an additive formula, \emph{Proc. Edinb. Math. Soc. (2)} {\bf 64} (2021), 279--297.
\item Chmieli\'{n}ski, Jacek and Khurana, Divya and Sain, Debmalya: Local approximate symmetry of {B}irkhoff-{J}ames orthogonality
in normed linear spaces, \emph{Results Math.} {\bf 76} (2021), Paper No. 136, 26.

@@

\item Choudhury, Projesh Nath and Eagambaram, N. and Sivakumar, K.
C. and Sushmitha, P.: On the matrix class {$Q_0$} and inverse monotonicity
properties of bordered matrices, \emph{Linear Algebra Appl.} {\bf 612} (2021), 206--222.
\item Choudhury, Projesh Nath and Kannan, M. Rajesh: Interval hulls of {$N$}-matrices and almost {$P$}-matrices, \emph{Linear Algebra Appl.} {\bf 617} (2021), 27--38.

@@

\item Choudhury, Projesh Nath and Sivakumar, K. C.: Matrices with positive semidefinite real part, \emph{Linear Multilinear Algebra} {\bf 69} (2021), 448--470.

@@

\item Datar, Ved and Jacob, Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual connections on collapsed
{$K3$} surfaces, \emph{J. Differential Geom.} {\bf 118} (2021), 223--296.
\item Datar, Ved and Seshadri, Harish and Song, Jian: Metric rigidity of {K}\"{a}hler manifolds with lower {R}icci
bounds and almost maximal volume, \emph{Proc. Amer. Math. Soc.} {\bf 149} (2021), 3569--3574.
\item Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane, \emph{Discrete Comput. Geom.} {\bf 65} (2021), 531--553.

@@

\item Deb, Prahllad: On unitary invariants of quotient {H}ilbert modules along
smooth complex analytic sets, \emph{Bull. Sci. Math.} {\bf 169} (2021), Paper No. 102977, 42.

@@

\item Dias, Kealey and Gupta, Subhojoy and Trnkova, Maria: Quadratic differentials, measured foliations, and metric
graphs on punctured surfaces, \emph{Illinois J. Math.} {\bf 65} (2021), 417--454.

@@

\item Ganguly, Pritam and Thangavelu, Sundaram: On the lacunary spherical maximal function on the {H}eisenberg
group, \emph{J. Funct. Anal.} {\bf 280} (2021), 108832, 32.
\item Ganguly, Pritam and Thangavelu, Sundaram: Theorems of {C}hernoff and {I}ngham for certain eigenfunction
expansions, \emph{Adv. Math.} {\bf 386} (2021), Paper No. 107815, 31.

@@

\item Ghosh, Mrinal K. and Suresh Kumar, K. and Pal, Chandan and
Pradhan, Somnath: Nonzero-sum risk-sensitive stochastic differential games with
discounted costs, \emph{Stoch. Anal. Appl.} {\bf 39} (2021), 306--326.

@@

\item Gupta, Subhojoy: Harmonic maps and wild {T}eichm\"{u}ller spaces, \emph{J. Topol. Anal.} {\bf 13} (2021), 349--393.

@@

\item Gupta, Subhojoy and Mj, Mahan: Meromorphic projective structures, grafting and the monodromy
map, \emph{Adv. Math.} {\bf 383} (2021), Paper No. 107673, 49.

@@

\item Hatui, Sumana and Singla, Pooja: On {S}chur multiplier and projective representations of
{H}eisenberg groups, \emph{J. Pure Appl. Algebra} {\bf 225} (2021), Paper No. 106742, 16.

@@

\item Khare, Apoorva and Pingali, Vamsi Pritham: On an asymptotic characterisation of {G}riffiths
semipositivity, \emph{Bull. Sci. Math.} {\bf 167} (2021), Paper No. 102956, 7.

@@

\item Khare, Apoorva and Rajaratnam, Bala: Differential calculus on the space of countable labelled
graphs, \emph{Adv. Oper. Theory} {\bf 6} (2021), Paper No. 12, 28.

@@

\item Khurana, Divya and Sain, Debmalya: Norm derivatives and geometry of bilinear operators, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 49, 19.

@@

\item Kreuzer, Martin and Patil, Dilip P.: Computational aspects of {B}urnside rings part {II}: important
maps, \emph{Beitr. Algebra Geom.} {\bf 62} (2021), 475--494.

@@

\item Lai, King-Fai and Longhi, Ignazio and Suzuki, Takashi and Tan,
Ki-Seng and Trihan, Fabien: On the {$\mu$}-invariants of abelian varieties over function
fields of positive characteristic, \emph{Algebra Number Theory} {\bf 15} (2021), 863--907.

@@

\item Manna, Ramesh and Shrivastava, Saurabh and Shuin, Kalachand: Weighted estimates for maximal functions associated with
finite type curves in {$\Bbb R^2$}, \emph{Nonlinear Anal.} {\bf 205} (2021), 112225, 24.

@@

\item Nandakumaran, A. K. and Sufian, Abu: Oscillating {PDE} in a rough domain with a curved interface:
homogenization of an optimal control problem, \emph{ESAIM Control Optim. Calc. Var.} {\bf 27} (2021), Paper No. S4, 37.
\item Nandakumaran, A. K. and Sufian, Abu: Strong contrasting diffusivity in general oscillating domains:
homogenization of optimal control problems, \emph{J. Differential Equations} {\bf 291} (2021), 57--89.

@@

\item Pingali, Vamsi Pritham and Varolin, Dror: Nonuniformly flat affine algebraic hypersurfaces, \emph{Nagoya Math. J.} {\bf 241} (2021), 1--43.
\item Poria, Anirudha: Uncertainty principles for the {O}pdam-{C}herednik transform
on modulation spaces, \emph{Integral Transforms Spec. Funct.} {\bf 32} (2021), 191--206.

@@

\item Pradhan, Somnath: Risk-sensitive ergodic control of reflected diffusion
processes in orthant, \emph{Appl. Math. Optim.} {\bf 83} (2021), 1739--1764.

@@

\item Roy, Saikat and Senapati, Tanusri and Sain, Debmalya: Orthogonality of bilinear forms and application to matrices, \emph{Linear Algebra Appl.} {\bf 615} (2021), 104--111.

@@

\item Sain, Debmalya: Orthogonality and smoothness induced by the norm derivatives, \emph{Rev. R. Acad. Cienc. Exactas F\'{\i}s. Nat. Ser. A Mat. RACSAM} {\bf 115} (2021), Paper No. 120, 10.
\item Sain, Debmalya and Bhunia, Pintu and Bhanja, Aniket and Paul,
Kallol: On a new norm on {$\Cal B(\Cal H)$} and its applications to
numerical radius inequalities, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 51, 25.
\item Sain, Debmalya and Mal, Arpita and Bhunia, Pintu and Paul,
Kallol: On numerical radius and {C}rawford number attainment sets of a
bounded linear operator, \emph{J. Convex Anal.} {\bf 28} (2021), 67--80.
\item Sain, Debmalya and Mal, Arpita and Mandal, Kalidas and Paul,
Kallol: On uniform {B}ishop-{P}helps-{B}ollob\'{a}s type approximations of
linear operators and preservation of geometric properties, \emph{J. Math. Anal. Appl.} {\bf 494} (2021), 124582, 22.

@@

\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On extreme contractions between real {B}anach spaces, \emph{Expo. Math.} {\bf 39} (2021), 33--47.

@@

\item Sebastian, Geethika and Daniel, Sukumar: A weaker {G}leason-{K}ahane-\.{Z}elazko theorem for modules and
applications to {H}ardy spaces, \emph{Colloq. Math.} {\bf 164} (2021), 273--282.
\item Sen, Jeet and Sain, Debmalya and Paul, Kallol: Orthogonality and norm attainment of operators in
semi-{H}ilbertian spaces, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 17, 12.
\item Sen, Jeet and Sain, Debmalya and Paul, Kallol: On approximate orthogonality and symmetry of operators in
semi-{H}ilbertian structure, \emph{Bull. Sci. Math.} {\bf 170} (2021), Paper No. 102997, 22.

@@

\item \'{A}lvarez-C\'{o}nsul, Luis and Garcia-Fernandez, Mario and
Garc\'{\i}a-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the {E}instein-{B}ogomol'nyi
equations, \emph{Math. Ann.} {\bf 379} (2021), 1651--1684.

@@

\item Addario-Berry, Louigi and Bhamidi, Shankar and Sen, Sanchayan: \href{https://doi.org/10.1002/rsa.20966}{A probabilistic approach to the leader problem in random
graphs}, \emph{Random Structures Algorithms} {\bf 58} (2021), 34--67.

@@

\item Adhikari, Saswata and Anoop, V. P. and Parui, Sanjay: \href{https://doi.org/10.1007/s11785-020-01068-1}{Existence of extremals of {D}unkl-type {S}obolev inequality
and of {S}tein-{W}eiss inequality for {D}unkl {R}iesz
potential}, \emph{Complex Anal. Oper. Theory} {\bf 15} (2021), Paper No. 28, 34.

@@

\item Anoop, V. P. and Parui, Sanjay: \href{https://doi.org/10.7153/mia-2021-24-10}{Improved fractional {H}ardy inequalities for {D}unkl gradient}, \emph{Math. Inequal. Appl.} {\bf 24} (2021), 129--155.
\item Arunkumar, G.: \href{https://doi.org/10.1016/j.jcta.2021.105492}{Chromatic symmetric function of graphs from {B}orcherds
algebras}, \emph{J. Combin. Theory Ser. A} {\bf 183} (2021), Paper No. 105492, 28.

@@

\item Balodi, Mamta and Banerjee, Abhishek and Ray, Samarpita: \href{https://doi.org/10.1007/s11856-021-2108-2}{Entwined modules over linear categories and {G}alois
extensions}, \emph{Israel J. Math.} {\bf 241} (2021), 623--692.

@@

\item Banerjee, Abhishek: \href{https://doi.org/10.1016/j.jpaa.2020.106595}{{$FI$}-modules over preadditive categories and torsion
theories}, \emph{J. Pure Appl. Algebra} {\bf 225} (2021), 106595, 29.

@@

\item Banerjee, Agnid and Garofalo, Nicola and Manna, Ramesh: \href{https://doi.org/10.1007/s12220-020-00487-y}{A strong unique continuation property for the heat operator
with {H}ardy type potential}, \emph{J. Geom. Anal.} {\bf 31} (2021), 5480--5504.

@@

\item Basak, Riju and Garg, Rahul and Thangavelu, Sundaram: \href{https://doi.org/10.1016/j.jfa.2021.109154}{Homogeneous {F}ourier and {W}eyl multipliers on {S}obolev
spaces related to the {H}eisenberg group}, \emph{J. Funct. Anal.} {\bf 281} (2021), Paper No. 109154, 45.

@@

\item Basu, Riddhipratim and Ganguly, Shirshendu and Hegde, Milind
and Krishnapur, Manjunath: \href{https://doi.org/10.1007/s11856-021-2135-z}{Lower deviations in {$\beta$}-ensembles and law of iterated
logarithm in last passage percolation}, \emph{Israel J. Math.} {\bf 242} (2021), 291--324.
\item Behera, Kiran Kumar: \href{https://doi.org/10.1016/j.laa.2021.03.025}{A generalized inverse eigenvalue problem and {$m$}-functions}, \emph{Linear Algebra Appl.} {\bf 622} (2021), 46--65.

@@

\item Bera, Sudip: \href{https://doi.org/10.1515/spma-2020-0130}{Enumeration of weighted paths on a digraph and block hook
determinant}, \emph{Spec. Matrices} {\bf 9} (2021), 197--211.
\item Bera, Sudip and Dey, Hiranya Kishore and Mukherjee, Sajal
Kumar: \href{https://doi.org/10.1007/s00373-020-02267-5}{On the connectivity of enhanced power graphs of finite groups}, \emph{Graphs Combin.} {\bf 37} (2021), 591--603.

@@

\item Bhattacharyya, Tirthankar and Das, B. Krishna and Sau,
Haripada: \href{https://doi.org/10.1093/imrn/rnz333}{Toeplitz operators on the symmetrized bidisc}, \emph{Int. Math. Res. Not. IMRN} {\bf } (2021), 8492--8520.

@@

\item Biswas, Anindya and Maitra, Anwoy: \href{https://doi.org/10.1016/j.jmaa.2021.125434}{A characterization of the bidisc by a subgroup of its
automorphism group}, \emph{J. Math. Anal. Appl.} {\bf 504} (2021), Paper No. 125434, 10.

@@

\item Carstensen, Carsten and Mallik, Gouranga and Nataraj, Neela: \href{https://doi.org/10.1093/imanum/drz071}{Nonconforming finite element discretization for semilinear
problems with trilinear nonlinearity}, \emph{IMA J. Numer. Anal.} {\bf 41} (2021), 164--205.

@@

\item Chattopadhyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan: \href{https://doi.org/10.1017/S0013091521000146}{Multiplicities, invariant subspaces and an additive formula}, \emph{Proc. Edinb. Math. Soc. (2)} {\bf 64} (2021), 279--297.
\item Chmieli\'{n}ski, Jacek and Khurana, Divya and Sain, Debmalya: \href{https://doi.org/10.1007/s00025-021-01437-y}{Local approximate symmetry of {B}irkhoff-{J}ames orthogonality
in normed linear spaces}, \emph{Results Math.} {\bf 76} (2021), Paper No. 136, 26.

@@

\item Choudhury, Projesh Nath and Eagambaram, N. and Sivakumar, K.
C. and Sushmitha, P.: \href{https://doi.org/10.1016/j.laa.2020.10.041}{On the matrix class {$Q_0$} and inverse monotonicity
properties of bordered matrices}, \emph{Linear Algebra Appl.} {\bf 612} (2021), 206--222.
\item Choudhury, Projesh Nath and Kannan, M. Rajesh: \href{https://doi.org/10.1016/j.laa.2021.01.005}{Interval hulls of {$N$}-matrices and almost {$P$}-matrices}, \emph{Linear Algebra Appl.} {\bf 617} (2021), 27--38.

@@

\item Choudhury, Projesh Nath and Sivakumar, K. C.: \href{https://doi.org/10.1080/03081087.2019.1602588}{Matrices with positive semidefinite real part}, \emph{Linear Multilinear Algebra} {\bf 69} (2021), 448--470.

@@

\item Datar, Ved and Jacob, Adam and Zhang, Yuguang: \href{https://doi.org/10.4310/jdg/1622743140}{Adiabatic limits of anti-self-dual connections on collapsed
{$K3$} surfaces}, \emph{J. Differential Geom.} {\bf 118} (2021), 223--296.
\item Datar, Ved and Seshadri, Harish and Song, Jian: \href{https://doi.org/10.1090/proc/15473}{Metric rigidity of {K}\"{a}hler manifolds with lower {R}icci
bounds and almost maximal volume}, \emph{Proc. Amer. Math. Soc.} {\bf 149} (2021), 3569--3574.
\item Datta, Basudeb and Gupta, Subhojoy: \href{https://doi.org/10.1007/s00454-019-00156-0}{Semi-regular tilings of the hyperbolic plane}, \emph{Discrete Comput. Geom.} {\bf 65} (2021), 531--553.

@@

\item Deb, Prahllad: \href{https://doi.org/10.1016/j.bulsci.2021.102977}{On unitary invariants of quotient {H}ilbert modules along
smooth complex analytic sets}, \emph{Bull. Sci. Math.} {\bf 169} (2021), Paper No. 102977, 42.

@@

\item Dias, Kealey and Gupta, Subhojoy and Trnkova, Maria: \href{https://doi.org/10.1215/00192082-8827639}{Quadratic differentials, measured foliations, and metric
graphs on punctured surfaces}, \emph{Illinois J. Math.} {\bf 65} (2021), 417--454.

@@

\item Ganguly, Pritam and Thangavelu, Sundaram: \href{https://doi.org/10.1016/j.jfa.2020.108832}{On the lacunary spherical maximal function on the {H}eisenberg
group}, \emph{J. Funct. Anal.} {\bf 280} (2021), 108832, 32.
\item Ganguly, Pritam and Thangavelu, Sundaram: \href{https://doi.org/10.1016/j.aim.2021.107815}{Theorems of {C}hernoff and {I}ngham for certain eigenfunction
expansions}, \emph{Adv. Math.} {\bf 386} (2021), Paper No. 107815, 31.

@@

\item Ghosh, Mrinal K. and Suresh Kumar, K. and Pal, Chandan and
Pradhan, Somnath: \href{https://doi.org/10.1080/07362994.2020.1796707}{Nonzero-sum risk-sensitive stochastic differential games with
discounted costs}, \emph{Stoch. Anal. Appl.} {\bf 39} (2021), 306--326.

@@

\item Gupta, Subhojoy: \href{https://doi.org/10.1142/S1793525320500156}{Harmonic maps and wild {T}eichm\"{u}ller spaces}, \emph{J. Topol. Anal.} {\bf 13} (2021), 349--393.

@@

\item Gupta, Subhojoy and Mj, Mahan: \href{https://doi.org/10.1016/j.aim.2021.107673}{Meromorphic projective structures, grafting and the monodromy
map}, \emph{Adv. Math.} {\bf 383} (2021), Paper No. 107673, 49.

@@

\item Hatui, Sumana and Singla, Pooja: \href{https://doi.org/10.1016/j.jpaa.2021.106742}{On {S}chur multiplier and projective representations of
{H}eisenberg groups}, \emph{J. Pure Appl. Algebra} {\bf 225} (2021), Paper No. 106742, 16.

@@

\item Khare, Apoorva and Pingali, Vamsi Pritham: \href{https://doi.org/10.1016/j.bulsci.2021.102956}{On an asymptotic characterisation of {G}riffiths
semipositivity}, \emph{Bull. Sci. Math.} {\bf 167} (2021), Paper No. 102956, 7.

@@

\item Khare, Apoorva and Rajaratnam, Bala: \href{https://doi.org/10.1007/s43036-020-00111-4}{Differential calculus on the space of countable labelled
graphs}, \emph{Adv. Oper. Theory} {\bf 6} (2021), Paper No. 12, 28.

@@

\item Khurana, Divya and Sain, Debmalya: \href{https://doi.org/10.1007/s43034-021-00134-9}{Norm derivatives and geometry of bilinear operators}, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 49, 19.

@@

\item Kreuzer, Martin and Patil, Dilip P.: \href{https://doi.org/10.1007/s13366-020-00520-9}{Computational aspects of {B}urnside rings part {II}: important
maps}, \emph{Beitr. Algebra Geom.} {\bf 62} (2021), 475--494.

@@

\item Lai, King-Fai and Longhi, Ignazio and Suzuki, Takashi and Tan,
Ki-Seng and Trihan, Fabien: \href{https://doi.org/10.2140/ant.2021.15.863}{On the {$\mu$}-invariants of abelian varieties over function
fields of positive characteristic}, \emph{Algebra Number Theory} {\bf 15} (2021), 863--907.

@@

\item Manna, Ramesh and Shrivastava, Saurabh and Shuin, Kalachand: \href{https://doi.org/10.1016/j.na.2020.112225}{Weighted estimates for maximal functions associated with
finite type curves in {$\Bbb R^2$}}, \emph{Nonlinear Anal.} {\bf 205} (2021), 112225, 24.

@@

\item Nandakumaran, A. K. and Sufian, Abu: \href{https://doi.org/10.1051/cocv/2020045}{Oscillating {PDE} in a rough domain with a curved interface:
homogenization of an optimal control problem}, \emph{ESAIM Control Optim. Calc. Var.} {\bf 27} (2021), Paper No. S4, 37.
\item Nandakumaran, A. K. and Sufian, Abu: \href{https://doi.org/10.1016/j.jde.2021.04.031}{Strong contrasting diffusivity in general oscillating domains:
homogenization of optimal control problems}, \emph{J. Differential Equations} {\bf 291} (2021), 57--89.

@@

\item Pingali, Vamsi Pritham and Varolin, Dror: \href{https://doi.org/10.1017/nmj.2019.2}{Nonuniformly flat affine algebraic hypersurfaces}, \emph{Nagoya Math. J.} {\bf 241} (2021), 1--43.
\item Poria, Anirudha: \href{https://doi.org/10.1080/10652469.2020.1813129}{Uncertainty principles for the {O}pdam-{C}herednik transform
on modulation spaces}, \emph{Integral Transforms Spec. Funct.} {\bf 32} (2021), 191--206.

@@

\item Pradhan, Somnath: \href{https://doi.org/10.1007/s00245-019-09606-w}{Risk-sensitive ergodic control of reflected diffusion
processes in orthant}, \emph{Appl. Math. Optim.} {\bf 83} (2021), 1739--1764.

@@

\item Roy, Saikat and Senapati, Tanusri and Sain, Debmalya: \href{https://doi.org/10.1016/j.laa.2020.12.032}{Orthogonality of bilinear forms and application to matrices}, \emph{Linear Algebra Appl.} {\bf 615} (2021), 104--111.

@@

\item Sain, Debmalya: \href{https://doi.org/10.1007/s13398-021-01060-0}{Orthogonality and smoothness induced by the norm derivatives}, \emph{Rev. R. Acad. Cienc. Exactas F\'{\i}s. Nat. Ser. A Mat. RACSAM} {\bf 115} (2021), Paper No. 120, 10.
\item Sain, Debmalya and Bhunia, Pintu and Bhanja, Aniket and Paul,
Kallol: \href{https://doi.org/10.1007/s43034-021-00138-5}{On a new norm on {$\Cal B(\Cal H)$} and its applications to
numerical radius inequalities}, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 51, 25.
\item Sain, Debmalya and Mal, Arpita and Bhunia, Pintu and Paul,
Kallol: On numerical radius and {C}rawford number attainment sets of a
bounded linear operator, \emph{J. Convex Anal.} {\bf 28} (2021), 67--80.
\item Sain, Debmalya and Mal, Arpita and Mandal, Kalidas and Paul,
Kallol: \href{https://doi.org/10.1016/j.jmaa.2020.124582}{On uniform {B}ishop-{P}helps-{B}ollob\'{a}s type approximations of
linear operators and preservation of geometric properties}, \emph{J. Math. Anal. Appl.} {\bf 494} (2021), 124582, 22.

@@

\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: \href{https://doi.org/10.1016/j.exmath.2019.09.004}{On extreme contractions between real {B}anach spaces}, \emph{Expo. Math.} {\bf 39} (2021), 33--47.

@@

\item Sebastian, Geethika and Daniel, Sukumar: \href{https://doi.org/10.4064/cm8015-9-2019}{A weaker {G}leason-{K}ahane-\.{Z}elazko theorem for modules and
applications to {H}ardy spaces}, \emph{Colloq. Math.} {\bf 164} (2021), 273--282.
\item Sen, Jeet and Sain, Debmalya and Paul, Kallol: \href{https://doi.org/10.1007/s43034-020-00104-7}{Orthogonality and norm attainment of operators in
semi-{H}ilbertian spaces}, \emph{Ann. Funct. Anal.} {\bf 12} (2021), Paper No. 17, 12.
\item Sen, Jeet and Sain, Debmalya and Paul, Kallol: \href{https://doi.org/10.1016/j.bulsci.2021.102997}{On approximate orthogonality and symmetry of operators in
semi-{H}ilbertian structure}, \emph{Bull. Sci. Math.} {\bf 170} (2021), Paper No. 102997, 22.

@@

\item \'{A}lvarez-C\'{o}nsul, Luis and Garcia-Fernandez, Mario and
Garc\'{\i}a-Prada, Oscar and Pingali, Vamsi Pritham: \href{https://doi.org/10.1007/s00208-020-01964-z}{Gravitating vortices and the {E}instein-{B}ogomol'nyi
equations}, \emph{Math. Ann.} {\bf 379} (2021), 1651--1684.
